Towards Reliable Machine Learning Deployments in the Cloud

### 2023-12-11 paper.tex

\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}

@@

\begin{abstract}
Considering the growing prominence of production-level AI and the threat of adversarial attacks that can poison a machine learning model against a certain label, evade classification, or reveal sensitive data about the model and training data to an attacker, adversaries pose fundamental problems to machine learning systems. Prior research has noted the need to extend beyond the normal train-test split paradigm for evaluating models due of the ease with which one can generally find adversarial counterexamples. Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem. Furthermore, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex. So, instead of this train-test split methodology, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and learning rate by using adversarial attacks to induce failures on a reference model architecture. We evaluate several GPU types and use Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. In this way, we can evaluate our model and optimize it in a single step, which provides a precise way to not only measure the effect of different hardware deployments but also of the model parameters. Using this technique, we demonstrate that newer, more-powerful hardware does increase model robustness, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
\cm{obviously, this needs to be written out formally, but this is a rough outline for now}
\subsection{Motivations}
\begin{itemize}
    \item \textbf{BIG} Data is the trend
    \item Costs are astronomical
    \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
    \item Other work relies on unreliable test/train split methodology
    \item Which means that cars, medical equipment is tested in the wild
\end{itemize}

\subsection{Research Questions}
Our goal is to answer three questions

\begin{itemize}
    \item What is relationship between latency, robustness, and deployment cost?
    \item What is the cheapest way to guarantee a certain response time and accuracy?
\end{itemize}

\subsection{Contributions}
\begin{itemize}
    \item Confirm previous work about the efficacy adversarial analysis for model selection
    \item Test the run-time behavior of several search algorithms
    \item Test several different cpu- and gpu- architectures
    \item Measure the monetary and power costs of model deployment with respect to the benign and adversarial survival times
    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of advesrarial robustness
\end{itemize}

@@

A classifier with model parameters, $\theta$, $K(x; \theta)$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization function without loss of generality.} an \textbf{objective} (or \textbf{loss}) \textbf{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the optimal loss value, $L^*$ is:
\[
L^*(y, K(x, \theta)) = \mathrm{argmin}_{\theta \in \Theta} y - K(x, \theta).
\]
From here, we can find the optimal configuration of the classifier by selecting the one that minimizes loss. In the case of neural-networks, however, this is non-trivial as the number of tunable parameters is often measured in the millions. Instead of finding an analytical solution to this equation, we often rely on \textbf{stochastic gradient descent}, which iteratively shuffles the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss, $-\nabla L(y, K(x, \theta))$, after some number of \textbf{epochs} (iterative random shufflings of the data), $m$, such that:
\begin{equation}
\theta_{m+1} := \theta_{m} - \eta \nabla_x L(y, K(x, \theta_m))
\label{eq:sgd}
\end{equation}
where $\eta$ is a \textbf{learning rate} that is tuned to the particular model.

\subsection{Adversarial Attacks}

In the context of machine learning, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit machine learning models. Adversarial attacks are designed to deceive or mislead the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or produce undesired outputs. That is, a successful attack is one in which the model outputs on unperturbed data $\hat{y}$ are not the same as the model outputs on perturbed data, $x^*$. That is \textbf{adversarial success} or \textbf{accelerated failure} is one in which:
\begin{equation}
\hat{y} \neq y^* = K(x^*, \theta)
\label{eq:adv_success}
\end{equation}
The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses. These attacks can occur during various stages of the machine learning pipeline, including during training, inference, or deployment.

\begin{itemize}
    \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying or ignoring certain inputs. Attackers carefully craft perturbations or modify the input features to mislead the model while still appearing similar to the original input \cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
    \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset. The goal is to influence the model's behavior during training so that it learns to make incorrect predictions or exhibit unwanted behaviors when presented with specific inputs \cite{biggio_poisoning_2013, saha2020hidden}.
    \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details. By observing the model's predictions or confidence scores for carefully crafted inputs, attackers can extract information that should ideally be kept private \cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
    \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs. Attackers utilize the model's responses to iteratively reconstruct or approximate training examples that are similar to the ones used during training \cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
\end{itemize}
One attack designed to induce failures as quickly as possible~\cite{fgm,meyers_aft} works by iterating over a set of samples, $x_0$,

$$
x_{i+1} = x_{i} + \eta \mathrm{~sgn~}(\nabla_x L(y, K(x, \theta))).
$$
In essence, this is stochastic gradient \textit{ascent}, the opposite process from model training.

@@

\subsubsection{Accuracy}
The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted machine learning model to misclassify or produce incorrect outputs \cite{meyers}. It measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textbf{robustness} against noise-induced failures. Throughout, we use the terminology \textbf{benign accuracy} to refer to the performance on the test set using unperturbed data. The benign accuracy is defined as
\begin{equation}
 \mathrm{Accuracy} = 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}}
\label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data \cite{}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{biggio_evasion_2013,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.
\ In addition, this method ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{}. Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples. Such that 
$$
y\neq\hat{y}\mathrm{~s.t.~}\| x^* - x \| \leq \varepsilon \leq \varepsilon_{max}
$$

@@

\subsubsection{Failure Rate}
 To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.} training time, inference time, attack generation time, etc.) and some covariates (\textit{e.g.} noise distance, model size, hardware resources) such that:
\[
h(t; \theta) :=  \frac{\textrm{False~Classifications}}{\textrm{Total~Time}}
\]
To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models~\cite{meyers_aft} that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
\[
S(t; x,y, \theta) := 1 - \int_{t=0}^{\infty} h(t;\theta) d \theta
\]

@@

@@

Because of the relatively small run-time requirements of this approach (when compared to testing against massive in-distribution test sets), this method could, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism. It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples. Furthermore, by isolating changes and testing them as quickly as possible, it's much easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test. To further increase development velocity, we can use these models to quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}. However, hyper-parameters are often drawn from continuous and infinite spaces, so it's impossible to exhaustively evaluate the search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds, meaning that a proper search would keep this dual-objective in mind. Luckily, the field of multi-objective search is well researched and analyze the run-time requirements for several popular choices below, each of which will be useful for different types of search spaces.

\begin{itemize}
    \item TPE Sampler
    \item NGAS2/3
    \item Bayesian Optimization
\end{itemize}

\subsection{Pareto Set}
In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{}. A subset of examples that maximize one or more objective criteria is called the \textbf{pareto front}~\cite{zitzler2008quality}. It has been shown that we can find an $\varepsilon$-approximation of this front $\mathcal{P}$ in $d$ dimensions using $(1/ \varepsilon)^d$ queries ~\cite{legriel2010approximating}. Table~\ref{tab:pareto} shows the required number of queries to get estimates within the $\varepsilon$-sphere of the true Pareto front. As we can see, it is critical to minimize the dimensionality of our search. So instead of optimizing for latency, training time, cost, accuracy, and adversarial success rate independently, we introduce several metrics in the next section.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Please add the following required packages to your document preamble:
% 
\begin{table}[t!]
\begin{tabular}{cl|llll|}
\cline{3-6}
                                           &   & \multicolumn{4}{c|}{$\varepsilon$}            \\ \cline{3-6} 
                                           &   & .1     & .05          & .01    & .001      \\ \hline
\multicolumn{1}{|c|}{\multirow{3}{*}{$d$}} & 1 & 10     & 20           & 100    & 1000      \\
\multicolumn{1}{|c|}{}                     & 2 & 100    & 400          & $10^4$ & $10^6$    \\
\multicolumn{1}{|c|}{}                     & 4 & $10^4$ & $1.6 * 10^5$ & $10^9$ & $10^{12}$ \\ \hline
\end{tabular}
\caption{This table shows the number of queries required to $\varepsilon-$ approximate the Pareto front, $\mathcal{P}$, in $d$ dimensions.}
\label{tab:pareto}
\end{table}

@@

We withheld 100 examples from both the test and train sets as the initial values for adversarial examples, which gives us two significant figures for this measurement. In addition, we measured the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the cost per hour for a particular hardware ($C$), and the power consumption ($P$) of each tested model and attack.

\subsection{Benign Success}
A \textit{success} can be thought of in both the adversarial and benign context, which are denoted with the subscripts $ben.,adv.$ throughout this work. Typically this is measured via the train/test methodology in which some subset of a benchmark dataset. However, this method has repeatedly shown itself to be an inadequate measure of real-world model performance, and is, at best, an optimistic best-case measure of the failure rate~\cite{croce_reliable_2020}. The benign success ratio is usually measured via the train/test split methodology mentioned in Section~\ref{train/test-split}.

\subsection{Adversarial Success}
A successful adversary, however, is one that is able to change the model's output from one class to another. For the benign case, we measure the test set accuracy as our success metric. However, we m

Furthermore, the computational difficulty of this task is often related to secondary optimization criteria~\cite{}, with a baseline of at least NP-Hard~\cite{madry2017towards}. Since many of the attacks have more success after a number of iterations\cite{fgm,deepfool,carlini_towards_2017,madry2017towards,hopskipjump}, it is appropriate to think about their success in terms of time.

@@

\subsubsection{Power}
The power consumption for a particular piece of hardware ($P_h$), measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
$$
    P_t = P_h \cdot T_t,
    \label{eq:cost_training}
$$
the power consumption during model inference is:
$$
    P_i = P_h \cdot T_i
    \label{eq:cost_inference}
$$
and the power consumption during attack generation is:
$$
    P_a = P_h \cdot T_a
$$

\subsection{Survival Time}
Correspondingly, we can talk about the expected survival time under optimistic, $S_{ben.}$ as well as under adverse (accelerated failure rate distribution), $S_{adv.}$. If we assume that the distribution of failures is uniform with respect to latency, a
$$
S_{ben.} := S(t_i; x, y, \theta) \mathrm{~s.t.~} \varepsilon = 0
$$
and
$$
S_{adv.} :=  S(t_i; x, y, \theta) \mathrm{~s.t.~} 0 < \varepsilon \leq \varepsilon_{max}
$$
\subsection{Dollars per Second}

@@

\section{Methods}
\subsection{Cloud Platform and Hardware}
\textcolor{red}{To conduct the experiments and have access to different types of hard, we utilized Google Cloud Platform (GCP). Six virtual machines running Container Optimized Operating System provided by GCP constitute our testbed. Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster that comprises of six worker nodes. Three worker nodes were responsible for running the monitoring platform such as Prometheus 2.47.2 and Grafana 10.2.0. These nodes were of the 'e2-medium' instance type provided by Google Cloud Platform. In total, we used three different GPU based on their availability. For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4' node.}

\textcolor{red}{To assess the energy consumption of Deckard deployed on a GKE, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}. This approach enables us to gather energy consumption data on granular level as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components. In essence, KEPLER uses extended Berkley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics. eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space. eBPF programs are invoked by the kernel when certain events, called hooks, occur. Examples of such hooks include system calls, network events. These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}.}
\begin{table}[]
\begin{tabular}{lllll}
                 & V100   & P100   & L4    &  \\
Cost (\$/hour)    & 2.55 & 1.60 & .81 &  \\
Power (Watts)           &        &        &       &  \\
Memory Bandwidth (GB/s) &        &        &       &

Costs were taken from \footnote{}
\label{tab:hardware}
\end{tabular}
\end{table}
\subsection{Software Pipeline}
\subsection{Datasets}
\subsection{Models}
\subsection{Attacks}
\subsection{Monetary Cost}
\subsection{Power}

>>>>

\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
\newcommand{\mr}[1]{\textit{{\color{red}#1}}}

@@

\begin{abstract}
Considering the growing prominence of production-level AI and the threat of adversarial attacks that can poison a machine learning model against a certain label, evade classification, or reveal sensitive data about the model and training data to an attacker, adversaries pose fundamental problems to machine learning systems. Prior research has noted the need to extend beyond the normal train-test split paradigm for evaluating models due of the ease with which one can generally find adversarial counterexamples. Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem. Furthermore, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex. So, instead of this train-test split methodology, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and learning rate by using adversarial attacks to induce failures on a reference model architecture. We evaluate several GPU types and use Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. In this way, we can evaluate our model and optimize it in a single step, which provides a precise way to not only measure the effect of different hardware deployments but also of the model parameters. Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
\end{abstract}

\begin{IEEEkeywords}
artificial intelligence, machine learning, adversarial AI, optimization, compliance
\end{IEEEkeywords}

\section{Introduction}
\subsection{Motivations}
\begin{itemize}
    % \item \textbf{BIG} Data is the trend
    % \item Costs are astronomical
    \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
    \item Other work relies on unreliable test/train split methodology
    \item Which means that cars, medical equipment is tested in the wild
\end{itemize}

Recently, artificial intelligence using neural networks has become a popular way to classify large amounts of data-- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. However, neural networks need huge amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. Furthermore, popular models like general purpose transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have hundreds of millions or billions of parameters, requiring equally large training datasets. Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. Luckily, Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. The newest version of this open-source LLM is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}. Given the immense cost of deploying modern neural networks, this raises serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be one in trillions~\cite{iso26262}. Collecting, labelling, and testing a new set of data for every software change-as required by law- would be prohibitively expensive. Therefore, a new evaluation methodology is required. As such, we propose an evaluation metholodgy, centered on the statistical field of survival analysis, which tests a model against `worst-case' input to verify the efficacy of one software or hardware decision over another. Then, we use this method to examine and minimize the deployment cost for a singular model architecture, measuring this in terms of both power and monetary cost. In short, our goal is to answer three questions.

\subsection{Research Questions}
Our goal is to answer three questions.
\begin{itemize}
    \item What is relationship between latency, robustness, and deployment cost?
    \item What is the cheapest way to guarantee a certain response time and accuracy?
    \item Does better hardware make better models?
\end{itemize}

However, before we can answer these questions, we need to model the asymptotic behavior of various architectural choices, develop a method for precisely measuring model performance without resorting to trillions of test samples, and find a metric (or metrics) that will set one model apart from the others with respect to both failure rate and deployment cost.

\subsection{Contributions}
\begin{itemize}
    \item We confirm previous work about the efficacy adversarial analysis for model selection
    \item We measure the power and monetary cost of deploying a model across three different hardware architectures.
    \item We combine survival analysis with adversarial analysis to build accelerated failure models to compare the effect of model parameter choices.
    \item We use a Tree Parzen Estimator to minimize deployment cost while maximizing accuracy.
    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of adversarial robustness.
\end{itemize}

@@

A classifier with model parameters, $\theta$, $K(x; \theta)$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization function without loss of generality.} an \textbf{objective} (or \textbf{loss}) \textbf{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the optimal loss value, $L^*$ is:
\[
L^*(y, K(x, \theta)) = \mathrm{argmin}_{\theta \in \Theta} y - K(x, \theta).
\]
From here, we can find the optimal configuration of the classifier by selecting the one that minimizes loss. In the case of neural-networks, however, this is non-trivial as the number of tunable parameters is often measured in the millions. Instead of finding an analytical solution to this equation, we often rely on \textbf{stochastic gradient descent}, which iteratively shuffles the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss, $-\nabla L(y, K(x, \theta))$, after some number of \textbf{epochs} (iterative random sampling of the data), $m$, such that:
\begin{equation}
\theta_{m+1} := \theta_{m} - \eta \nabla_x L(y, K(x, \theta_m))
\label{eq:sgd}
\end{equation}
where $\eta$ is a \textbf{learning rate} that is tuned to the particular model.

\subsection{Learning Rate Selection}
\label{learning_rate}
\cm{TODO}
\begin{itemize}
    \item Much work has gone into this~\cite{}.
    \item A good learning rate will give us training times that are linear w.r.t sample size ~\cite{}
    \item Will depend on the batch size and number of epochs (define epochs) ~\cite{}
    \item The best batch size will depend on the memory bandwidth of the GPU~\cite{}
    \item That bandwidth is not guaranteed in on-demand cloud environments~\cite{}
    \item Hardware is charged by the hour, so minimizing training/inference times will reduce the costs of deployment.
\end{itemize}

\subsection{Adversarial Attacks}
\label{attacks}
In the context of machine learning, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit machine learning models. Adversarial attacks are designed to deceive or mislead the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or produce undesired outputs. That is, a successful attack is one in which the model outputs on unperturbed data $\hat{y}$ are not the same as the model outputs on perturbed data, $x'$. That is \textbf{adversarial success} or \textbf{accelerated failure} is one in which:
\begin{equation}
\hat{y} \neq y^* = K(x', \theta)
\label{eq:adv_success}
\end{equation}
Additionally, we can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textbf{adversarial accurracy}. The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses. These attacks can occur during various stages of the machine learning pipeline, including during training, inference, or deployment.

\cm{This itemize section could be cut and reduced to a couple sentences.}
\begin{itemize}
    \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying or ignoring certain inputs. Attackers carefully craft perturbations or modify the input features to mislead the model while still appearing similar to the original input \cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
    \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset. The goal is to influence the model's behavior during training so that it learns to make incorrect predictions or exhibit unwanted behaviors when presented with specific inputs \cite{biggio_poisoning_2013, saha2020hidden}.
    \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details. By observing the model's predictions or confidence scores for carefully crafted inputs, attackers can extract information that should ideally be kept private \cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
    \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs. Attackers utilize the model's responses to iteratively reconstruct or approximate training examples that are similar to the ones used during training \cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
\end{itemize}
One attack designed to induce failures as quickly as possible~\cite{fgm} works by applying noise to a set of samples, $x$, to generate adversarial examples, $x'$, such that:

\begin{equation}
x' = x + \eta \mathrm{~sgn~}(\nabla_x L(y, K(x, \theta))).
\label{eq:fgm}
\end{equation}
In essence, this is stochastic gradient \textit{ascent}, the opposite process from model training (stochastic gradient \textit{descent}).

@@

\subsubsection{Accuracy}
The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted machine learning model to misclassify or produce incorrect outputs \cite{meyers}. It measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textbf{robustness} against noise-induced failures. Throughout, we use the terminology \textbf{benign accuracy} to refer to the performance on the test set using unperturbed data. The benign accuracy is defined as
\begin{equation}
 \mathrm{Accuracy} = 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}}
\label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data \cite{}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{biggio_evasion_2013,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}. In addition, this method ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{}. Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples, such that 
$$
y\neq\hat{y}\mathrm{~s.t.~}\| x' - x \| \leq \varepsilon \leq \varepsilon_{max}
$$

@@

\subsubsection{Failure Rate}
 To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.} training time, inference time, attack generation time, etc.) and some covariates (\textit{e.g.} noise distance, model size, hardware resources) such that:
\[
h(t; \theta) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t}
\]
where $\mathbb{P}$ is a probability and $\Delta t$ is a time interval. To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models~\cite{meyers_aft} that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
\[
S(t; x,y, \theta) := 1 - \int_{t=0}^{\infty} h(t;\theta) d \theta
\]

@@

\subsection{Pareto Set}
\cm{This section could probably be cut without too much lost.}
In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{}. A subset of examples that maximize one or more objective criteria is called the \textbf{pareto front}~\cite{zitzler2008quality}. It has been shown that we can find an $\varepsilon$-approximation of this front $\mathcal{P}$ in $d$ dimensions using $(1/ \varepsilon)^d$ queries ~\cite{legriel2010approximating}. Table~\ref{tab:pareto} shows the required number of queries to get estimates within the $\varepsilon$-sphere of the true Pareto front. As we can see, it is critical to minimize the dimensionality of our search. So instead of optimizing for latency, training time, cost, accuracy, and adversarial success rate independently, we introduce several metrics in the next section.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Please add the following required packages to your document preamble:
% 
\begin{table}[h!]
\begin{tabular}{cl|llll|}
\cline{3-6}
                                           &   & \multicolumn{4}{c|}{$\varepsilon$}            \\ \cline{3-6} 
                                           &   & .1     & .05          & .01    & .001      \\ \hline
\multicolumn{1}{|c|}{\multirow{3}{*}{$d$}} & 1 & 10     & 20           & 100    & 1000      \\
\multicolumn{1}{|c|}{}                     & 2 & 100    & 400          & $10^4$ & $10^6$    \\
\multicolumn{1}{|c|}{}                     & 4 & $10^4$ & $1.6 * 10^5$ & $10^9$ & $10^{12}$ \\ \hline
\end{tabular}
\caption{This table shows the number of queries required to $\varepsilon-$ approximate the Pareto front, $\mathcal{P}$, in $d$ dimensions.}
\label{tab:pareto}
\end{table}

@@

Because of the relatively small run-time requirements of this approach (when compared to testing against massive in-distribution test sets), this method could, for example, act as a unit test in machine learning applications rather than relying on full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism. It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples. Furthermore, by isolating changes and testing them as quickly as possible, it's much easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars or MRI machines) to effectively test. To further increase development velocity, we can use these models to quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard \cite{iso26262}. However, hyper-parameters are often drawn from continuous and infinite spaces, so it's impossible to exhaustively evaluate the search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds, meaning that a proper search would keep this dual-objective in mind. Luckily, the field of multi-objective search is well researched and analyze the run-time requirements for several popular choices below, each of which will be useful for different types of search spaces. We chose the Tree-structure Parzen Estimator (TPE) because of it's ability to work on mini-batches~\cite{}, in distributed settings~\cite{}, and while optimizing multiple objectives~\cite{} in a feasible number of trials ~\cite{}.

@@

We withheld 100 examples from both the test and train sets as the initial values for adversarial examples, which gives us two significant figures for this measurement. In addition, we measured the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the cost per hour for a particular hardware ($C$), and the power consumption ($P$) of each tested model and attack, as well as the benign and adversarial accuracies (see: Secs.~\ref{eq:acc} and ~\ref{eq:adv_success}).

\subsection{Accuracy}
We measured both the benign accuracy and the adversarial accuracy, which reflect the normal test-set accuracy and the test-set accuracy in the presence of additive noise in the direction that maximizes loss.

% \subsection{Benign Success}
% A \textit{success} can be thought of in both the adversarial and benign context, which are denoted with the subscripts $ben.,adv.$ throughout this work. Typically this is measured via the train/test methodology in which some subset of a benchmark dataset. However, this method has repeatedly shown itself to be an inadequate measure of real-world model performance, and is, at best, an optimistic best-case measure of the failure rate~\cite{croce_reliable_2020}. The benign success ratio is usually measured via the train/test split methodology mentioned in typical in the literature.

% \subsection{Adversarial Success}
% A successful adversary, however, is one that is able to change the model's output from one class to another. For the benign case, we measure the test set accuracy as our success metric. However, we m

% Furthermore, the computational difficulty of this task is often related to secondary optimization criteria~\cite{}, with a baseline of at least NP-Hard~\cite{madry2017towards}. Since many of the attacks have more success after a number of iterations\cite{fgm,deepfool,carlini_towards_2017,madry2017towards,hopskipjump}, it is appropriate to think about their success in terms of time.

@@

\subsubsection{Power}
The power consumption for a particular piece of hardware ($P_h$), measured in Watts (Joules per second), can be thought of similarly such that the total power consumption of model training is
$$
    P_t = P_h \cdot T_t,
    \label{eq:power_training}
$$
the power consumption during model inference is:
$$
    P_i = P_h \cdot T_i
    \label{eq:power_inference}
$$
and the power consumption during attack generation is:
$$
    P_a = P_h \cdot T_a
    \label{eq:power_attack}
$$

\subsection{Survival Time}
Correspondingly, we can talk about the expected survival time under optimistic, $S_{ben.}$ as well as under adverse (accelerated failure rate distribution), $S_{adv.}$. If we assume that the distribution of failures is uniform with respect to latency, a
$$
S_{ben.} := S(t_i; x, y, \theta) \mathrm{~s.t.~} \varepsilon = 0
$$
and
$$
S_{adv.} :=  S(t_i; x, y, \theta) \mathrm{~s.t.~} 0 < \varepsilon \leq \varepsilon_{max}
$$
\subsection{Relative Cost to an Attacker}
In security analysis, it's routine to think in optimistic terms for both the attacker and defender. As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see: Eq.~\ref{eq:fgm}) which adds noise of a specified magnitude to some samples in the direction that maximizes loss. If the cost to a model builder ($C_t$) is much larger than the attacker ($C_a$), then it's clear that a configuration.

@@

\section{Methods}
\subsection{Cloud Platform and Hardware}
To conduct the experiments and have access to different types of hard, we utilized Google Cloud Platform (GCP). Six virtual machines running Container Optimized Operating System provided by GCP constitute our testbed. Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0,  we created a cluster that comprises of six worker nodes. Three worker nodes were responsible for running the monitoring platform such as Prometheus 2.47.2 and Grafana 10.2.0. These nodes were of the 'e2-medium' instance type provided by Google Cloud Platform. In total, we used three different GPU based on their availability. For both, P100 and V100 GPUs, we used 'n1-standard-2' type for the nodes and for L4  we used 'g2-standard-4' node.
To assess the energy consumption of the experiments deployed on a GKE, we employed Kubernetes Efficient Power Level Exporter (KEPLER) as our measurement tool~\cite{amaral2023kepler}. This approach enables us to gather energy consumption data on granular level as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components. In essence, KEPLER uses extended Berkley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics. eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space. eBPF programs are invoked by the kernel when certain events, called hooks, occur. Examples of such hooks include system calls or network events. These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}. A diagram of the cloud architecture can be found in Fig.~\ref{fig:architecture}. Finally, to meet our goal of developing a cost-effective model evaluation technique, we restricted all of our experiments to a single one-thousand United States dollar research grant from Google.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{plots/architecture.pdf}
    \caption{Cloud Architecture Diagram}
    \label{fig:architecture}
\end{figure*}

For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a pareto-optimal result~\cite{} for the TPE algorithm, within some expected error bounds (see: Tab.~\ref{tab:pareto}). We used three optimization criteria-- benign accuracy, training time, and adversarial accuracy seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Fig.~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data.
